Online {\IterComp}

### 2017-09-15 work.tex
work minor
Work

    Figure~\ref{fig:work-vs-O0time} shows the correlation of the work metric ($\Delta W$) with runtime on instances of the unoptimized \texttt{susan\_c} benchmark.
    Each point represents the execution of a single input, from a total of 1,000 inputs.
    The correlation coefficient is $0.99$, and the mean absolute percentage error (MAPE) is only about 3.5\%.
    This result suggests that the new metric correlates much better than either execution time or IPC.

>>>>

    Figure~\ref{fig:work-vs-O0time} shows the correlation of the work metric ($\Delta W$) with runtime on instances of the unoptimized
    \texttt{susan\_c} benchmark. Each point represents the execution of a single input, from a total of 1,000 inputs. The correlation
    coefficient is $0.99$, and the mean absolute percentage error (MAPE) is only about 3.5\%. This result suggests that the new efficiency
    metric correlates much better with speedup than either execution time or IPC.
